%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Vedic Nerd - Resume LaTeX Template
%
% Original author:
% Ganesh Mohan (http://about.me/ganesh.mohan)
%
% Github repository:
% https://github.com/ganesh2shiv/resume-latex-template
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{article}

\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[T1]{fontenc}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{url}
\usepackage{hyperref}
% DEFINITIONS FOR RESUME

\textheight=10in
\pagestyle{fancy}
\raggedright
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\setlength{\hoffset}{-2pt}
\setlength{\footskip}{20pt}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

\newcommand{\contact}[3]{
\vspace*{5pt}
\begin{center}
{\large \scshape {#1}}\\
\vspace{3pt}
#2 
\vspace{2pt}
#3
\end{center}
\vspace*{-8pt}
}

\newcommand{\header}[1]{{
\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} 
\lineunder
}

\newcommand{\lineunder}{
\vspace*{-8pt} \\ \hspace*{-18pt} 
\hrulefill \\
}

\newcommand{\content}{
\vspace*{2pt}%
}

\newcommand{\college}[5]{\vspace*{2pt}% 
#1 \hfill #2 \\ #3 \hfill #4
\vspace*{5pt}
}

\newcommand{\school}[4]{
\textbf{#1} \labelitemi #2 \hfill #3 \\ #4 \vspace*{5pt}
}

\newcommand{\employer}[4]{{
\vspace*{2pt}%
\textbf{#1} - #2 \hfill #3\\ #4 \vspace*{2pt}}
}

\newcommand{\project}[4]{{
\vspace*{2pt}% 
\textbf{#1} #2 \hfill #3\\ \textit{#4} \vspace*{2pt}}
}

\renewcommand{\labelitemi}{
$\vcenter{\hbox{\tiny$\bullet$}}$\hspace*{3pt}
}

\renewcommand{\labelitemii}{
$\vcenter{\hbox{\tiny$\bullet$}}$\hspace*{-3pt}
}

\newenvironment{bullet-list-major}{
\begin{list}{\labelitemii}{\setlength\leftmargin{3pt} 
\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}
}

\newenvironment{bullet-list-minor}{
\begin{list}{\labelitemii}{\setlength\leftmargin{15pt} 
\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}
}

%\cfoot{
%Last updated: December 16, 2015
%}

\rfoot{
Page $\thepage\hspace*{3pt}\vert\hspace*{3pt}\pageref{LastPage}$
}

% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-65pt}

\begin{center}
    {\large \scshape{Krishna Vaidyanathan}}
\end{center}
    Ph: +1-226-978-2760\hfill \href{mailto:krishna.v.psg@outlook.com}{krishna.v.psg@outlook.com} \\
\vspace{15pt}

\header{Current Position}
    \content{Software Developer at Oracle NetSuite.}

%\vspace*{4pt}%
%\header{Areas of Interest}
%Reconfiguration problems, parameterized algorithms, and graph coloring. 

\vspace*{4pt}%
\header{Education}
    \college{\textbf{University of Waterloo}, Waterloo, Canada}{Sep 2015 -- Aug 2017}
    {\textit{M.Math (Thesis), Computer Science}}{}\\

    \college{\textbf{PSG College of Technology}, Coimbatore, India}{Jun 2010 -- May 2015}
    {\textit{Integrated M.Sc, Theoretical Computer Science}}{}\\

\vspace*{4pt}%
\header{Industry Experience}
  \employer{Software Developer}{Oracle NetSuite,
        Toronto}{Nov 2018 -- current}{}
	\begin{bullet-list-minor}
	\item Developing in Java+Kotlin/Oracle SQL for the domain of warehouse management.
	\item Involved in all aspects of agile software development.
    \end{bullet-list-minor}

    \employer{Full Stack Developer}{Coinsquare Mining,
        Toronto}{May 2018 -- Aug 2018}{}
	\begin{bullet-list-minor}
	\item Developed from scratch and managed an app (backend: Django; frontend: React) to buy and monitor
orders, using Celery, on \texttt{\href{www.nicehash.com}{NiceHash}};  this lead to increased profitability. 
	\item Added merged-mining support to the open source library \texttt{\href{https://github.com/UNOMP/node-merged-pool}{node-merged-pooler}}; this lead to a potential increase in profit at no additional cost.
    \end{bullet-list-minor}

    \employer{Backend Engineer}{BenchSci,
        Toronto}{Sep 2017 -- April 2018}{}
	\begin{bullet-list-minor}
	\item Managed a web crawler; parallelized the crawler leading to a 10X speed
increase.
	\item Designed webpages using Django and React; helped decouple the frontend
from the backend leading to increased code reusability.
	\item Wrote and optimized queries for neo4j; increased the speed of
queries by 5X.
	\item Interfaced with (and created a few) RESTful APIs.
    \end{bullet-list-minor}

    \employer{Software Development Engineer Intern}{Amazon Development Center,
        Chennai}{Jan 2015 -- July,
        2015}{}
	\begin{bullet-list-minor}
        \item Developed an internal tool to static analyze codebases by
            generating a graph of dependencies and isolating sections of the
            code that is affected by check-ins.
        \item Worked on Facebook's pfff tool and added features to enrichen the
            graph generated by pfff.
        \item Ported graph from pfff to TitanDB, a graph database, and wrote
            queries to derive insights from it.
        \item Code: \url{https://github.com/krishnavaidy/pfff}
    \end{bullet-list-minor}

\vspace*{4pt}%
\header{Research Experience}
\employer{Research Assistant}{University of Waterloo, Canada}{Sep, 2015 --
      Aug, 2017}{\textbf{Supervisor:} Prof. Naomi Nishimura}
\begin{bullet-list-minor}
\item Formulated problems in reconfiguration of colorings - specifically acyclic
and equiable colorings - and developed algorithms and complexity results for the
same.
\end{bullet-list-minor}

\vspace*{4pt}%
\header{Publications}
\begin{bullet-list-major}
\item Tesshu Hanaka, Takehiro Ito, Haruka Mizuta, Benjamin Moore, Naomi
Nishimura, Vijay Subramanya, \textbf{Krishna Vaidyanathan}. \textit{``Reconfiguring
spanning and induced subgraphs".} Computing and Combinatorics 438 (2018).
\item \textbf{Krishna Vaidyanathan}. \textit{``Reconfiguring Graph Colorings".} MS thesis. University of Waterloo (2017).
\item Robin Cohen, Alan Tsang, \textbf{Krishna Vaidyanathan}, Haotian Zhang. \textit{``Analyzing Opinion Dynamics in Online Social Networks".} BigDIA (Big Data and Information Analytics) (2016).
\item Jasine  Babu,  L.  Sunil  Chandran, \textbf{Krishna  Vaidyanathan}.
\textit{``Rainbow matchings in strongly edge-colored graphs".} Discrete Mathematics 338.7 (2015).
\end{bullet-list-major}

\vspace*{4pt}%
\header{Technical Skills}
\begin{tabular}{l l l}

\textbf{Languages}&: & Java, Python, Kotlin, JavaScript, Shell\\
\textbf{Platforms}&:  & Linux, Windows\\
\textbf{Tools}&:     &Oracle/SQL, neo4j, React, Django, Docker\\
\textbf{Cloud}&:     &AWS, DigitalOcean, Azure, GCP
\end{tabular}

%\newpage
%\vspace*{-20pt}

\vspace*{4pt}%
\header{Awards}
    \begin{bullet-list-major}
    \item Awarded the \textbf{Outstanding TA Award} by the \textit{University of Waterloo} in 2017.
    \item Adjudged the \textbf{Best All Rounder} by \textit{PSG College of Technology} in 2015.  
    \end{bullet-list-major}

\end{document}
