%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Vedic Nerd - Resume LaTeX Template
%
% Original author:
% Ganesh Mohan (http://about.me/ganesh.mohan)
%
% Github repository:
% https://github.com/ganesh2shiv/resume-latex-template
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{article}

\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[T1]{fontenc}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{url}
\usepackage{hyperref}
% DEFINITIONS FOR RESUME

\textheight=10in
\pagestyle{fancy}
\raggedright
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\setlength{\hoffset}{-2pt}
\setlength{\footskip}{20pt}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

\newcommand{\contact}[3]{
\vspace*{5pt}
\begin{center}
{\LARGE \scshape {#1}}\\
\vspace{3pt}
#2 
\vspace{2pt}
#3
\end{center}
\vspace*{-8pt}
}

\newcommand{\header}[1]{{
\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} 
\lineunder
}

\newcommand{\lineunder}{
\vspace*{-8pt} \\ \hspace*{-18pt} 
\hrulefill \\
}

\newcommand{\content}{
\vspace*{2pt}%
}

\newcommand{\college}[5]{\vspace*{2pt}% 
#1 \hfill #2 \\ #3 \hfill #4
\vspace*{5pt}
}

\newcommand{\school}[4]{
\textbf{#1} \labelitemi #2 \hfill #3 \\ #4 \vspace*{5pt}
}

\newcommand{\employer}[4]{{
\vspace*{2pt}%
\textbf{#1} - #2 \hfill #3\\ #4 \vspace*{2pt}}
}

\newcommand{\project}[4]{{
\vspace*{2pt}% 
\textbf{#1} #2 \hfill #3\\ \textit{#4} \vspace*{2pt}}
}

\renewcommand{\labelitemi}{
$\vcenter{\hbox{\tiny$\bullet$}}$\hspace*{3pt}
}

\renewcommand{\labelitemii}{
$\vcenter{\hbox{\tiny$\bullet$}}$\hspace*{-3pt}
}

\newenvironment{bullet-list-major}{
\begin{list}{\labelitemii}{\setlength\leftmargin{3pt} 
\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}
}

\newenvironment{bullet-list-minor}{
\begin{list}{\labelitemii}{\setlength\leftmargin{15pt} 
\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}
}

%\cfoot{
%Last updated: December 16, 2015
%}

\rfoot{
Page $\thepage\hspace*{3pt}\vert\hspace*{3pt}\pageref{LastPage}$
}

% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-44pt}

\contact{Krishna Vaidyanathan}{}
{(+1) 2269782760\labelitemi \href{mailto:kvaidyan@uwaterloo.ca}{kvaidyan@uwaterloo.ca}
    \labelitemi
    \url{https://cs.uwaterloo.ca/~kvaidyan}}
\vspace{15pt}
\header{Current Position}
    \content{
Second year student of the M.Math program at the Cherition School of Computer
Science, University of Waterloo, Canada.}

\vspace*{4pt}%
\header{Areas of Interest}
Reconfiguration problems, parameterized algorithms, and graph coloring. 

\vspace*{4pt}%
\header{Education}
    \college{\textbf{University of Waterloo}, Waterloo, Canada}{Sep 2015 -- May 2017 (expected)}
    {\textit{M.Math, Computer Science}}{CGPA: 90.20/100}\\

    \college{\textbf{PSG College of Technology}, Coimbatore, India}{Jun 2010 -- May 2015}
    {\textit{Integrated M.Sc, Theoretical Computer Science}}{CGPA: 8.62/10}\\

\vspace*{4pt}%
\header{Research Experience}
\employer{Project Assistant}{University of Waterloo, Canada}{Jan, 2016 -- July,
    2016}{\textbf{Supervisor:} Prof. Robin Cohen}
\begin{bullet-list-minor}
\item Extended a course project on Opinion Dynamics in Agent Research to a
    paper.
\end{bullet-list-minor}

  \employer{Research Assistant}{University of Waterloo, Canada}{Sep, 2015 --
      present}{\textbf{Supervisor:} Prof. Naomi Nishimura}
\begin{bullet-list-minor}
\item Working on reconfiguration problems in graph coloring. 
\end{bullet-list-minor}

\employer{Summer Intern}{Indian Statistical Institute,
    Chennai, India}{May, 2014 -- July, 2014}{\textbf{Supervisor:} Dr. Mathew C. Francis}
\begin{bullet-list-minor}
\item Worked on a few problems in contact graphs of L-shapes in the plane and $B_{k}$-VPG graphs.
\end{bullet-list-minor}

\employer{Research Intern}{Indian Institute of Science, Bangalore, India}{May,
    2013 -- Nov, 2014}{\textbf{Supervisor:} Prof. L. Sunil Chandran}
\begin{bullet-list-minor}
\item Investigated rainbow matchings in the class of strongly edge-colored graphs and found a bound on the maximum rainbow matchings in terms of its minimum degree.
\end{bullet-list-minor}

\vspace*{4pt}%
\header{Industry Experience}
    \employer{Software Development Engineer Intern}{Amazon Development Center,
        Chennai}{Jan 2015 -- July,
        2015}{}
	\begin{bullet-list-minor}
        \item Worked on an internal tool to static analyze codebases by
            generating a graph of dependencies and isolating sections of the code
            that is affected by check-ins. 
        \item Worked extensively on Facebook's pfff tool and
            adding features to enrichen the graph generated by pfff.
        \item Also ported the graph from facebook/pfff to TitanDB, a graph
            database, and wrote queries to derive insights from it.
        \item Code: \url{https://github.com/krishnavaidy/pfff}
    \end{bullet-list-minor}

\vspace*{4pt}%
\header{Publications}
\begin{bullet-list-major}
\item Robin Cohen, Alan Tsang, Krishna Vaidyanathan, Haotian Zhang. 
    \textit{``Analyzing Opinion Dynamics in Online Social Networks". Accepted, to appear in 
        BigDIA (Big Data and Information Analytics).} 
\item Jasine  Babu,  L.  Sunil  Chandran, Krishna  Vaidyanathan.
    \textit{``Rainbow matchings in strongly edge-colored graphs".} Discrete Mathematics 338.7 (2015):  1191-1196.
\end{bullet-list-major}

\vspace*{4pt}%
\header{Technical Skills}
\begin{tabular}{l l l}

\textbf{Languages}&: & OCaml, Python.\\
\textbf{Backend}&:	& MySQL.\\
\textbf{Platform}&:  & Linux, Windows.\\
\textbf{Tools}&:     &MATLAB, LaTex, Coq.\\
\end{tabular}

\vspace*{4pt}%
\header{Courses Credited}
    \begin{bullet-list-major}
    \item \textbf{CS 666:} Design and Analysis of Algorithms - Instructor: Prof.
        Bin Ma
    \item \textbf{CS 798:} Algorithmic Spectral Graph Theory - Instructor: Prof.
        Lap Chi Lau
    \item \textbf{CS 854:} Advanced Topics in Computer Systems: Experimental OS
        Techniques - Instructor: Prof. Martin Karsten
    \item \textbf{CS 886:} Trust Modeling and Online Social Networks -
        Instructor: Prof. Robin Cohen
    \item \textbf{CS 798:} Software Foundations (Coq) - Instructor: Prof.
        Prabhakar Ragde
    \end{bullet-list-major}

\newpage
\vspace*{-20pt}

\vspace*{4pt}%
\header{Achievements}
    \begin{bullet-list-major}
    \item Recipient of the ``University of Waterloo Graduate Scholarship".
    \item Adjudged the ``Best All Rounder" for the class of 2015 by PSG College of
        Technology. 
    \item Selected for the ``Indian Academy of Science Summer Research Fellowship".
    \end{bullet-list-major}

\vspace*{4pt}%
\header{Extra Curricular Activities}
    \begin{bullet-list-major}
    \item ``Graduate Ambassador" for the Cheriton School of Computer Science,
        University of Waterloo. I answered queries from prospective graduate
        students about course load, research areas, student life, etc.
    \item Certified by the Lifesaving Society to perform ``Emergency First Aid".
    \item Completed levels N5 and N4 in the ``Japanese Language Proficiency Test".
    \end{bullet-list-major}


\end{document}
